\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}



\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{#1}
}

\newcommand{\resumeItemPrefix}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItemPrefix{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\cdot$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://carey.li}{\Large Carey Li}} & Email : \href{mailto:hello@carey.li}{hello@carey.li}\\
  \href{https://carey.li}{carey.li} $\cdot$ \href{https://github.com/cry}{github.com/cry} $\cdot$ \href{https://linkedin.com/in/definitelycarey}{linkedin.com/in/definitelycarey} & Mobile : +852 5743 5883 \\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Jane Street}{Hong Kong}
      {Production Engineer}{Jan 2020 - Present}
      \resumeItemListStart
        \resumeItem{Proposed and lead a project to overhaul sheet downloading infrastructure, improving observability and reliability of these processes whilst speeding up download times significantly \emph{(e.g. mirrors that used to take more than 2 hours now complete in 15 minutes)}.}
        \resumeItem{Implemented a SFTPv3 client with support for parallelized mirroring, directory traversals with regex pre-matching and file prioritization. All together, these features allow for remote sites to be mirrored efficiently, cutting down the average mirror time by a factor of 4 or more.}
        \resumeItem{Reworked the alerting and support story around mirroring processes, addressing blind spots and removing the need for expert knowledge to diagnose issues \emph{(e.g. common errors now come with a detailed list of possible faults and remediation steps)}.}
        \resumeItem{Designed and implemented a sheet health web interface allowing operations to quickly check the status of sheets required for back-office processes in a timely and self-service manner. The interface is now used daily in every office, saving 6+ hours a week spent on inter-team asks on sheet statuses.}
        \resumeItem{Extended the sheet web interface with support for editing sheet details, allowing users to update sheets without requiring knowledge of OCaml nor assistance from production engineers, saving 3+ hours a week.}
      \resumeItemListEnd

    \resumeSubheading
      {Optiver Asia Pacific}{Sydney, Australia}
      {Software Developer Intern}{Feb 2019 -- Jun 2019}
      \resumeItemListStart
        \resumeItem{Developed tooling to enable fleet-wide continuous deployment, with 90\% of applications continuously deployed.}
        \resumeItem{Created web dashboards to surface statistics on package deployments and state.}
        \resumeItem{Managed rollouts of continuous deployment tooling through Ansible.}
      \resumeItemListEnd
      
    \resumeSubSubheading
     {Application Engineer Intern}{Nov 2018 -- Feb 2019}
     \resumeItemListStart
        \resumeItem{Implemented a process status reporting framework, surfacing metrics on over 3000 applications.}
        \resumeItem{Modernised legacy components of process control tooling, improving service reliability and quality.}
     \resumeItemListEnd

    \resumeSubheading
      {Nasdaq (SMARTS Trade Surveillance)}{Sydney, Australia}
      {DevOps Engineer (Contract)}{Mar 2018 -- Nov 2018}
      \resumeItemListStart  
          \resumeItem{Containerised existing CI pipelines, reducing test times from 30 minutes to 3.}
          \resumeItem{Created and maintained Puppet modules to effectively manage infrastructure.}
          \resumeItem{Packaged modern software tools to supersede versions available on CentOS 6.}
      \resumeItemListEnd
      
    \resumeSubSubheading
     {DevOps Intern}{Nov 2017 -- Mar 2018}
     \resumeItemListStart
        \resumeItem{Implemented an automated regression testing framework, improving test coverage.}
        \resumeItem{Developed proof of concepts for new internal tools, enabling clients to self-validate data, and reducing turnaround times from weeks to hours.}
     \resumeItemListEnd


  \resumeSubHeadingListEnd
  
  %-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of New South Wales}{Sydney, Australia}
      {B.Sc. (Computer Science, majoring in Security Engineering);  WAM 81.42}{2017 -- 2019}
  \resumeSubHeadingListEnd

  
%-----------EDUCATION-----------------
\section{Distinctions}
  \resumeSubHeadingListStart
    \resumeSubheading
      {PyCon 2019}{}
      {\href{https://www.youtube.com/watch?v=l0Sazyzs1IY}{Speaker (Using Python, Flask and Docker to teach Web Pentesting)}}{2019}
  \resumeSubheading
      {\href{https://www.cyberchallenge.com.au/}{Cyber Challenge Australia (CySCA)}}{}
      {Overall Second Place}{2018}
  \resumeSubheading
      {Facebook Bug Bounty Program }{}
      {Denial of Service Vulnerability in Facebook Messenger}{2016}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
%\section{Projects}
%  \resumeSubHeadingListStart
%    \resumeSubItem{QuantSoftware Toolkit}
%      {Open source python library for financial data analysis and machine learning for finance.}
%    \resumeSubItem{Github Visualization}
%      {Data Visualization of Git Log data using D3 to analyze project trends over time.}
%    \resumeSubItem{Recommendation System}
%      {Music and Movie recommender systems using collaborative filtering on public datasets.}
%    \resumeSubItem{Mac Setup}
%      {Book that gives step by step instructions on setting up developer environment on Mac OS.}
%  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
